\begin{longtable}{@{} >{\raggedright}p{5.25in} >{\raggedleft}X @{}}

\hangindent=5ex \textbf{Michael J. Koontz}, Victoria Scholl, Anna Spiers, Megan Cattau, and John Adler. Integrating drone-derived geometric and spectral information with the National Ecological Observatory Network: A framework and guide for self teaching. & [\textcolor{blue}{\href{https://github.com/mikoontz/neon-drone-workflow}{GitHub}}] \tabularnewline

\hangindent=5ex \textbf{Michael J. Koontz}, Zachary L. Steel, Andrew M. Latimer, and Malcolm P. North. Initial wildfire suppression efforts select for more extreme fuel and climate burning conditions in Sierra Nevada forests.  & [\textcolor{blue}{\href{https://github.com/mikoontz/selection-by-suppression}{GitHub}}] \tabularnewline

\hangindent=5ex Jennifer Balch, John Abatzoglou, Park Williams, Max Joseph, Joseph McGlinchy, Megan Cattau, \textbf{Michael J. Koontz}. The global contribution of nighttime burning to fire regimes in a changing climate. & \tabularnewline

\hangindent=5ex Meagan F. Oldfather, \textbf{Michael J. Koontz}, Daniel F. Doak, and David D. Ackerly. Testing the leading-trailing edge paradigm for range shift predictions with experimental demography. & \tabularnewline

\hangindent=5ex Emilio A. Laca, Steven P. Lee, Jan Ng, Mikaela M. Provost, Jessica Rudnick, Linda Mendez-Barriento, Derek J. Young, \textbf{Michael J. Koontz}, Anne Todgham, Ben Sacks, and Elizabeth Sturdy. Holistic review in graduate admissions for an R1 STEM program: I. Statistical method to weight desirable applicant qualities and minimize reviewer effects. & \tabularnewline

\hangindent=5ex Anna Braswell, Virginia Iglesias, Jennifer K. Balch, Max B. Joseph, Caitlin M. Shane, Stefan Leyk, Matthew W. Rossi, Chelsea Nagy, Joseph McGlinchy, Megan Cattau, Lise Ann St. Denis, \textbf{Michael J. Koontz}, Adam L. Mahood, Travis M. Williams, Brian R. Johnson, and William R. Travis. Chang\tabularnewline

\hangindent=5ex Yufang Jin, Margarita Huesca Martinez, \textbf{Michael J. Koontz}, Yuhan Huang, Andrew Latimer, Susan Ustin, and Simon J. Hook. Tree mortality detection and assessment using AVIRIS imaging spectroscopy data in Sierra Nevada. &


\end{longtable}


% these are some collaborations that will hopefully be revived
%\hangindent=5ex \textbf{Michael J. Koontz} and Jeff C. Schank. An agent based model simulation of the outbreak behavior of the western pine beetle during the 2012 to 2016 Sierra Nevada megadrought. & [\textcolor{blue}{\href{https://github.com/mikoontz/wpb-forest-structure-abm}{GitHub}}] \tabularnewline

%\hangindent=5ex Jens T. Stevens, \textbf{Michael J. Koontz}, and Chhaya M. Werner.
%Local effects of aspect on vegetation productivity in California.  & \tabularnewline
%
%\hangindent=5ex \textbf{Michael J. Koontz} and Ruth A. Hufbauer.
%Several, small introductions of individuals to a novel environment facilitate adaptation by mitigating genetic load. & [\textcolor{blue}{\href{https://github.com/mikoontz/ppp-adaptation}{GitHub}}] \tabularnewline



% This code includes affiliations, but perhaps that is too verbose.
%\textbf{Michael J. Koontz}$^{1}$, Chhaya M. Werner$^{1}$, Stephen E. Fick$^{2}$, Malcolm P. North$^{1,3}$, and Andrew M. Latimer$^{1}$. Local variability of vegetation structure increases forest resilience to wildfire
%$^{1}$University of California, Davis, $^{2}$U.S. Geological Survey, Southwest Biological Science Center, $^{3}$U.S. Forest Service, Pacific Southwest Research Station
%\textcolor{blue}{\href{https://github.com/mikoontz/remote-sensing-resistance}{https://github.com/mikoontz/remote-sensing-resistance}}  & \tabularnewline

%\textbf{Michael J. Koontz}$^{1}$, Andrew M. Latimer$^{1}$, Leif A. Mortenson$^{2}$, Chris J. Fettig$^{2}$, Connie I. Millar $^{2}$, and Malcolm P. North$^{1,2}$ 
%\emph{The effect of spatial variability of forest structure on the severity of a tree-killing insect} 
%$^{1}$University of California, Davis, $^{2}$U.S. Forest Service, Pacific Southwest Research Station 
%\textcolor{blue}{\href{https://github.com/mikoontz/local-structure-wpb-severity}{https://github.com/mikoontz/local-structure-wpb-severity}}  & \tabularnewline

%Jens T. Stevens$^{1}$, \textbf{Michael J. Koontz}$^{2}$, and Chhaya M. Werner$^{2}$ 
%\emph{Local effects of aspect on vegetation productivity in California.}\tabularnewline
%$^{1}$U.S. Geological Survey, Southwest Biological Science Center, $^{2}$University of California, Davis  & \tabularnewline

%\textbf{Michael J. Koontz}$^{1}$ and Ruth A. Hufbauer$^{2}$ 
%\emph{Several, small introductions of individuals to a novel environment facilitate adaptation by mitigating genetic load} 
%$^{1}$University of California, Davis, $^{2}$Colorado State University   & \tabularnewline


