\begin{longtable}{@{} >{\raggedright}p{6.25in} >{\raggedleft}X @{}}

\hangindent=5ex \textbf{Koontz, Michael J.}, Victoria M. Scholl, Anna I. Spiers, Megan E. Cattau, John Adler, Joe McGlinchy, Tristan Goulden, Brett A. Melbourne, Jennifer K. Balch. Democratizing macroecology: integrating uncrewed aerial systems with the National Ecological Observatory Network. Submitted to \emph{Ecosphere}. [\textcolor{blue}{\href{https://github.com/mikoontz/neon-drone-workflow}{GitHub}}] & \tabularnewline

\hangindent=5ex Balch, Jennifer K., John T. Abatzoglou*, Maxwell B. Joseph*, \textbf{Michael J. Koontz*}, Adam L. Mahood*, Joseph McGlinchy*, Megan E. Cattau, A. Park Williams. Warming weakens the nighttime barrier to global fire. Revisions requested for \emph{Nature}. 
\newline *Equally contributing second authors & \tabularnewline

\hangindent=5ex Iglesias, Virginia, Anna E. Braswell, Maxwell B. Joseph, Caitlin McShane, Matthew W. Rossi, Megan E. Cattau, \textbf{Michael J. Koontz}, Joe McGlinchy, R. Chelsea Nagy, Jennifer K. Balch, Stefan Leyk, and William R. Travis. Risky development: Increasing exposure to natural hazards in the United States. Revisions submitted to \emph{Earth's Future}. & \tabularnewline

\hangindent=5ex Joseph, Maxwell B., Anna I. Spiers, \textbf{Michael J. Koontz}, Nayani Ilangakoon, Kylen Solvik, Nathan Quarderer, Joe McGlinchy, Victoria M. Scholl, Lise St. Denis, Chelsea Nagy, Anna Braswell, Matthew W. Rossi, Lauren Herwehe, Leah Wasser, Megan E. Cattau, Virginia Iglesias, Adam Mahood, Fangfang Yao, Stefan Leyk, and Jennifer K. Balch. Ten simple rules for working with high resolution remote sensing data.  \newline \emph{EcoEvoRxiv} preprint: https://osf.io/kehqz/ & \tabularnewline

\end{longtable}
