\begin{longtable}{@{} >{\raggedright}p{5.25in} >{\raggedleft}X @{}}
\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, Chhaya M. Werner, Stephen E. Fick, and Andrew M. Latimer. 2019. Local forest structure variability increases resilience to wildfire in dry western U.S. coniferous forests. Accepted in \emph{Ecology Letters}. \newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.32942/osf.io/k72ye & 2019 \tabularnewline

\hangindent=5ex Parks, Sean A., Lisa M. Holsinger, \textbf{Michael J. Koontz}, Luke Collins, Ellen Whitman, Marc-Andr\'e Parisien, Rachel A. Loehman, Jennifer L. Barnes, Jean-Fran\c{c}ois Bourdon, Jonathan Boucher, Yan Boucher, Anthony C. Caprio, Adam Collingwood, Ron J. Hall, Jane Park, Lisa B. Saperstein, Charlotte Smetanka, Rebecca J. Smith, and Nick Soverel. 2019. Giving ecological meaning to satellite-derived fire severity metrics across North American forests. \emph{Remote Sensing}. 11: 1735. https://doi.org/10.3390/rs11141735 \newline \textsuperscript{*}Editor's Choice article & 2019 \tabularnewline

\hangindent=5ex Smithers, Brian V., Meagan F. Oldfather, \textbf{Michael J. Koontz}, Jim Bishop, Catie Bishop, Jan Nachlinger, and Seema N. Sheth. 2019. Community turnover by composition and climatic affinity across scales in an alpine system. \emph{American Journal of Botany}. https://doi.org/10.1002/ajb2.1376 & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Meagan F. Oldfather, Brett A. Melbourne, and Ruth A. Hufbauer. 2018. Parsing propagule pressure: Number, not size, of introductions drives colonization success in a novel environment. \emph{Ecology and Evolution}. 8 (16): 8043-8054. https://doi.org/10.1002/ece3.4226 & 2018 \tabularnewline

\hangindent=5ex Steel, Zachary L., \textbf{Michael J. Koontz}, and Hugh D. Safford. 2018. The changing landscape of wildfire: Burn pattern trends and implications for California's yellow pine and mixed conifer forests. \emph{Landscape Ecology}. 33 (7): 1159-1176. https://doi.org/10.1007/s10980-018-0665-5 & 2018 \tabularnewline

\hangindent=5ex Oldfather, Meagan F., Matthew N. Britton, Prahlad D. Papper, \textbf{Michael J. Koontz}, Michelle M. Halbur, Celeste Dodge, Alan L. Flint, Lorraine E. Flint, and David D. Ackerly. 2016. Effects of topoclimatic complexity on the composition of woody plant communities. \emph{AoB Plants}. 8: plw049. https://doi.org/10.1093/aobpla/plw049 & 2016 \tabularnewline

\hangindent=5ex Hufbauer, Ruth A., Marianna Sz\"ucs, Emily Kasyon, Courtney Youngberg, \textbf{Michael J. Koontz}, Christopher Richards, Ty Tuff, and Brett A. Melbourne. 2015. Reply to Wootton and Pfister: The search for general context should include synthesis with laboratory model systems. \emph{Proceedings of the National Academy of Sciences}. 112 (44): E5904. https://doi.org/10.1073/pnas.1517210112 & 2015 \tabularnewline

\hangindent=5ex Hufbauer, Ruth A., Marianna Sz\"ucs, Emily Kasyon, Courtney Youngberg, \textbf{Michael J. Koontz}, Christopher Richards, Ty Tuff, and Brett A. Melbourne. 2015. Three types of rescue can avert extinction in a changing environment. \emph{Proceedings of the National Academy of Sciences}. 112 (33): 10557-10562. https://doi.org/10.1073/pnas.1504732112 & 2015 \tabularnewline

\hangindent=5ex Cole, Rebecca J., Creighton M. Litton, \textbf{Michael J. Koontz}, and Rhonda K. Loh. 2012. Vegetation recovery 16 years after feral pig removal from
a wet Hawaiian forest. \emph{Biotropica}. 44: 463-471. https://doi.org/10.1111/j.1744-7429.2011.00841.x & 2012 \tabularnewline

\end{longtable}
