\begin{longtable}{@{}>{\raggedright}p{5.25in} @{} >{\raggedleft}X@{}}

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christopher J. Fettig, and Malcolm P. North. 2020-08-03. The effect of spatial variability of forest structure on severity of a tree-killing insect. Ecological Society of America Annual Meeting. \emph{Remote Conference}. & 2020 \tabularnewline

\hangindent=5ex Parks, Sean, Lisa Holsinger, \textbf{Michael J. Koontz}, Luke Collins, Ellen Whitman, Marc-André Parisien and Rachel Loehman. 2020-08-03. Giving ecological meaning to satellite-derived fire severity metrics across North American forests. Ecological Society of America Annual Meeting. \emph{Remote Conference}. & 2020 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, Chhaya M. Werner, Stephen E. Fick, and Andrew M. Latimer. 2019-06-06. Local variability in forest structure increases resilience of dry, western US forests to wildfire. Flash talk to EROS Director CJ Loria. Boulder, CO. & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christopher J. Fettig, Constance I. Millar, and Malcolm P. North. 2018-09-20. The effect of spatial variability of forest structure on severity of a tree-killing insect. MtnClim Conference. Gothic, CO. & 2018 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Chhaya M. Werner, Stephen E. Fick, and Malcolm P. North. 2018-08-09. Greater variability in local vegetation structure increases forest resilience to wildfire. Ecological Society of America Annual Meeting. New Orleans, LA. & 2018 \tabularnewline

\hangindent=5ex Lee, Stephen P., Jan Ng, Ash T. Zemenick, Mikaela M. Provost, Carlos A. Ruvalcaba, Derek J. N. Young, Emilio Laca, \textbf{Michael J. Koontz}, Jessica Rudnick, and Elizabeth J. Sturdy. 2018-03-03. Evolution toward holistic review in the Ecology Graduate Program at University of California, Davis -- Part I: Design and implementation of a system to evaluate applicants. 10th Annual Understanding Interventions Meeting. Baltimore, MD. & 2018 \tabularnewline

\hangindent=5ex Ng, Jan, \textbf{Michael J. Koontz}, Jessica Rudnick, Elizabeth J. Sturdy, Ash T. Zemenick, Steven P. Lee, Mikaela M. Provost, Carlos A. Ruvalcaba, Derek J. N. Young, and Emilio Laca. 2018-03-03. Evolution toward holistic review in the Ecology Graduate Program at UC Davis -- Part II: Methods for evaluating progress. 10th Annual Understanding Interventions that Broaden Participation in Science Careers Meeting. Baltimore, MD. & 2018 \tabularnewline

\hangindent=5ex Oldfather, Meagan F., Brian Smithers, \textbf{Michael J. Koontz}, Jan Nachlinger, Catie Bishop, Jim Bishop, and Constance I. Millar. 2018-02-02. Alpine plant community-climate relationships across elevation gradients in the White Mountains, California. California Native Plant Society Conservation Conference. Los Angeles, CA. & 2018 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, and Andrew M. Latimer. 2016-10-17. Spatial heterogeneity of vegetation increases forest resistance to wildfire, and modern forests have a high potential for large, stand-replacing events. MtnClim Conference. Leavenworth, WA. & 2016 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2014-09-24. The eco-evolutionary consequences of multiple introductions for colonizing individuals. BSPM Departmental Seminar and Thesis Defense. Fort Collins, CO. & 2014 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.} and Ruth A. Hufbauer. 2014-08-08. The consequences of multiple introductions for colonizing individuals. Ecological Society of America Annual Meeting. Sacramento, CA. & 2014 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.} and Ruth A. Hufbauer. 2014-02-19. Parsing propagule pressure: The role of multiple introductions in the colonization of novel habitats. Front Range Student Ecology Symposium. Fort Collins, CO. & 2014 \tabularnewline

\end{longtable}
