\begin{longtable}{@{}>{\raggedright}p{5.25in} @{} >{\raggedleft}X@{}}

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christiopher J. Fettig, and Malcolm P. North. 2021-11-09. Drone-enabled forestry: drivers of tree mortality across multiple scales in a hot drought. Yosemite Forum. & 2021 \\ (remote) \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2020-09-14. Understanding where wildfires and insects kill trees using drones and satellites. CIRES @ Home. https://www.youtube.com/watch?v=HOgBQKSuhu8 & 2020 \\ (remote) \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer\textsuperscript{*}, Leif A. Mortenson, Christopher J. Fettig, Malcolm P. North. 2019-11-14. Differential response of a tree-killing bark beetle to forest structure across a gradient of climatic water deficit. California Forest Pest Council Annual Meeting. Davis, CA. \newline \textsuperscript{*}Presenting author & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christiopher J. Fettig, and Malcolm P. North. 2019-04-30: Differential response of a tree-killing bark beetle to forest structure across a gradient of climatic water deficit. Intermountain Drone Ecology Network workshop, Boulder, CO. & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, Christopher J. Fettig, Leif A. Mortenson, Constance I. Millar, Malcolm P. North. 2018-03-22. Using drones to link spatial structure of forests and insect outbreaks. University of California Cooperative Extension North Coast Forest Health Meeting. Eureka, CA. & 2018 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Christopher J. Fettig, Leif A. Mortenson, Constance I. Millar, Malcolm P. North. 2017-11-15. Using drones to go beyond stand density: Spatial features of western pine beetle-attacked forests. California Forest Pest Council Annual Meeting. Davis, CA. & 2017

\end{longtable}
