\begin{longtable}{@{}>{\raggedright}p{5.25in} @{} >{\raggedleft}X@{}}

\hangindent=5ex \textbf{Koontz, Michael J.}, Katharyn Duffy, and Hugh D. Safford. 2024-11-12. Synthesizing fire regime departure with open accessible science for resilient forest management. Climate Resilience Webinar. Hosted by South Korea National Institute of Ecology. & 2024 \\ (remote) \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Katharyn Duffy, and Hugh D. Safford. 2024-09-14. Synthesizing fire regime departure with open accessible science for resilient forest management. MtnClim2024. Tahoe City, CA, USA & 2024 \\ \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2024-08-28. From Software to Satellites: Harnessing Big Data for Wildfire Resilience. Webinar and panel discussion. Hosted by the Climate \& Wildfire Institute. & 2024 \\ (remote)  \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Amy DeCastro, Malcolm P. North, Jennifer K. Balch, and Andrew M. Latimer. 2023-12-05. Fine-scale weather, fuel, topography, and human drivers of explosive fire spread in California. 10th International Fire Ecology and Management Congress. Monterey, CA, USA & 2023 \\ \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2023-08-10. Harmonizing field, drone, and satellite data to monitor forest pests at management-relevant scales. Ecological Society of America Annual Meeting. Organized Oral Session: New approaches to age-old problems: data science for pest ecology at the landscape scale. Portland, OR, USA. & 2023 \\  \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2023-03-09. Democratizing macroecology with advances in technology, cyberinfrastructure, and education. Earth and Biological Systems Directorate at Pacific Northwest National Laboratory. Richland, WA, USA. & 2023 \\  \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christopher J. Fettig, and Malcolm P. North. 2021-11-09. Drone-enabled forestry: drivers of tree mortality across multiple scales in a hot drought. Yosemite Forum. & 2021 \\ (remote) \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}. 2020-09-14. Understanding where wildfires and insects kill trees using drones and satellites. CIRES @ Home. https://www.youtube.com/watch?v=HOgBQKSuhu8 & 2020 \\ (remote) \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer\textsuperscript{*}, Leif A. Mortenson, Christopher J. Fettig, Malcolm P. North. 2019-11-14. Differential response of a tree-killing bark beetle to forest structure across a gradient of climatic water deficit. California Forest Pest Council Annual Meeting. Davis, CA, USA. \newline \textsuperscript{*}Presenting author & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christopher J. Fettig, and Malcolm P. North. 2019-04-30. Differential response of a tree-killing bark beetle to forest structure across a gradient of climatic water deficit. Intermountain Drone Ecology Network workshop, Boulder, CO, USA. & 2019 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, Christopher J. Fettig, Leif A. Mortenson, Constance I. Millar, Malcolm P. North. 2018-03-22. Using drones to link spatial structure of forests and insect outbreaks. University of California Cooperative Extension North Coast Forest Health Meeting. Eureka, CA, USA. & 2018 \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Andrew M. Latimer, Christopher J. Fettig, Leif A. Mortenson, Constance I. Millar, Malcolm P. North. 2017-11-15. Using drones to go beyond stand density: Spatial features of western pine beetle-attacked forests. California Forest Pest Council Annual Meeting. Davis, CA, USA. & 2017

\end{longtable}
