\begin{longtable}{@{} >{\raggedright}p{6.10in} >{\raggedleft}X @{}}

\hangindent=5ex \textbf{Koontz, M.J.}, A.M. Latimer, L.A. Mortenson, C.J. Fettig, and M. P. North. 2021. Cross-scale interaction of host tree size and climatic water deficit governs bark beetle-induced tree mortality. \emph{Nature Communications}. 12: 129. \href{https://doi.org/10.1038/s41467-020-20455-y}{10.1038/s41467-020-20455-y}
\newline GitHub repository: \href{https://github.com/mikoontz/local-structure-wpb-severity}{mikoontz/local-structure-wpb-severity}
\newline + Investigated forest disturbance dynamics across scales by developing novel, end-to-end drone workflow to locate, measure, and classify >400,000 trees
\newline + Set new drone ecology benchmarks for area sampled (9 km\textsuperscript{2} of forest) and open science (1.25 TB of data/code publicly shared) & \tabularnewline

\hangindent=5ex Balch, J.K., J.T. Abatzoglou*, M.B. Joseph*, \textbf{M.J. Koontz*}, A.L. Mahood*, J. McGlinchy*, M.E. Cattau, and A.P. Williams. 2022. Warming weakens the nighttime barrier to global fire. \emph{Nature}. 602. 442-448. \href{https://doi.org/10.1038/s41586-021-04325-1}{10.1038/s41586-021-04325-1} *Equally contributing second authors
\newline GitHub repository: \href{https://github.com/earthlab/warming-weakens-the-nighttime-barrier-to-global-fire}{earthlab/warming-weakens-the-nighttime-barrier-to-global-fire} 
\newline + Led key geospatial data analytics to link changing wildfire activity and atmospheric conditions over hours and decades at a global scale
\newline + Deployed AWS EC2 instances to process 500GB of active fire data from GOES and MODIS, and 13 million hourly weather measurements from ERA5
& \tabularnewline

\hangindent=5ex \textbf{Koontz, M.J.}, V.M. Scholl, A.I. Spiers, M.E. Cattau, J. Adler, J. McGlinchy, T. Goulden, B.A. Melbourne, and J.K. Balch. Democratizing macroecology: integrating unoccupied aerial systems with the National Ecological Observatory Network. Accepted in \emph{Ecosphere}. 
\newline GitHub repository: \href{https://github.com/mikoontz/neon-drone-workflow}{mikoontz/neon-drone-workflow} 
\newline + Led a group of academic, government, and industry experts in creating a mental model for using drones for ecology research
\newline + Provide sample imagery and code for processing data from drones and integrating with the National Ecological Observatory Network
& \tabularnewline

\hangindent=5ex \textbf{Koontz, M.J.}, M.P. North, C.M. Werner, S.E. Fick, and A.M. Latimer. 2020. Local forest structure variability increases resilience to wildfire in dry western U.S. coniferous forests. \emph{Ecology Letters}. 23 (3): 483-494. \href{https://doi.org/10.1111/ele.13447}{10.1111/ele.13447} 
\newline GitHub repository: \href{https://github.com/mikoontz/remote-sensing-resistance}{mikoontz/remote-sensing-resistance}
\newline + Engineered creative geospatial analysis to provide ecosystem-wide, empirical support for a key landscape ecology hypothesis
\newline + Used Google Earth Engine to programmatically measure local forest structure variability and fire severity at broad scales & \tabularnewline

\end{longtable}