\begin{longtable}{@{} >{\raggedright}p{6.10in} >{\raggedleft}X @{}}

\hangindent=5ex 16. \textbf{Koontz, Michael J.}, Victoria M. Scholl, Anna I. Spiers, Megan E. Cattau, John Adler, Joe McGlinchy, Tristan Goulden, Brett A. Melbourne, and Jennifer K. Balch. Democratizing macroecology: integrating unoccupied aerial systems with the National Ecological Observatory Network. \emph{Ecosphere}. 13: e4206.
\newline GitHub repository: https://github.com/mikoontz/neon-drone-workflow   
\newline I contributed to conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, project administration, resources, software, supervision, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 15. Balch, Jennifer K., John T. Abatzoglou*, Maxwell B. Joseph*, \textbf{Michael J. Koontz*}, Adam L. Mahood*, Joseph McGlinchy*, Megan E. Cattau, and A. Park Williams. 2022. Warming weakens the nighttime barrier to global fire. \emph{Nature}. 602: 442-448. \href{https://doi.org/10.1038/s41586-021-04325-1}{https://doi.org/10.1038/s41586-021-04325-1}
\newline *Equally contributing second authors   
\newline I contributed to data curation, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 14. Young, Derek J. N., \textbf{Michael J. Koontz}, and Jonah M. Weeks. 2022. Optimizing aerial imagery collection and processing parameters for drone-based individual tree mapping in structurally complex conifer forests. \emph{Methods in Ecology and Evolution}. 13: 1447-1463. \href{https://doi.org/10.1111/2041-210X.13860}{https://doi.org/10.1111/2041-210X.13860}   
\newline I contributed to conceptualization, methodology, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 13. \textbf{Koontz, Michael J.}, Andrew M. Latimer, Leif A. Mortenson, Christopher J. Fettig, and Malcolm P. North. 2021. Cross-scale interaction of host tree size and climatic water deficit governs bark beetle-induced tree mortality. \emph{Nature Communications}. 12: 129. \href{https://doi.org/10.1038/s41467-020-20455-y}{https://doi.org/10.1038/s41467-020-20455-y}
\newline *Editor's Highlight in Climate Change Impacts %: https://www.nature.com/collections/hcfhgcahdc https://web.archive.org/web/20210818132826/https://www.nature.com/collections/hcfhgcahdc/
% \newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.32942/osf.io/jz964
\newline GitHub repository: \href{https://github.com/mikoontz/local-structure-wpb-severity}{https://github.com/mikoontz/local-structure-wpb-severity}   
\newline I contributed to conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, project administration, resources, software, supervision, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 12. Oldfather, Meagan F., \textbf{Michael J. Koontz}, Daniel F. Doak, and David D. Ackerly. 2021. Range dynamics mediated by compensatory life stage responses to experimental climate manipulations. \emph{Ecology Letters}. 24 (4): 772-280. \href{https://doi.org/10.1111/ele.13693}{https://doi.org/10.1111/ele.13693}
\newline GitHub repository: https://github.com/meaganfoldfather/experimental-ivesia-ipms   
\newline I contributed to formal analysis, investigation, resources, software, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 11. Nagy, Chelsea R., Jennifer K. Balch, and 118 co-authors. 2021. Harnessing the NEON data revolution to advance open environmental science with a diverse and data capable community. \emph{Ecosphere}. 12 (12): e03833. \href{https://doi.org/10.1002/ecs2.3833}{https://doi.org/10.1002/ecs2.3833}   
\newline I contributed to conceptualization, review, and editing. & \tabularnewline

\hangindent=5ex 10. Iglesias, Virginia, Anna E. Braswell, Maxwell B. Joseph, Caitlin McShane, Matthew W. Rossi, Megan E. Cattau, \textbf{Michael J. Koontz}, Joe McGlinchy, R. Chelsea Nagy, Jennifer K. Balch, Stefan Leyk, and William R. Travis. 2021. Risky development: increasing exposure to natural hazards in the United States. \emph{Earth's Future}. 9 (7): e2020EF001795. \href{https://doi.org/10.1029/2020EF001795}{https://doi.org/10.1029/2020EF001795}   
\newline I contributed to conceptualization, data curation, formal analysis, investigation, methodology, software, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 9. \textbf{Koontz, Michael J.}, Malcolm P. North, Chhaya M. Werner, Stephen E. Fick, and Andrew M. Latimer. 2020. Local forest structure variability increases resilience to wildfire in dry western U.S. coniferous forests. \emph{Ecology Letters}. 23 (3): 483-494. \href{https://doi.org/10.1111/ele.13447}{https://doi.org/10.1111/ele.13447} 
\newline GitHub repository: \href{https://github.com/mikoontz/remote-sensing-resistance}{https://github.com/mikoontz/remote-sensing-resistance}   
\newline I contributed to conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, project administration, resources, software, supervision, validation, visualization, writing the original draft, review, and editing. & \tabularnewline
% \newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.32942/osf.io/k72ye & \tabularnewline

\hangindent=5ex 8. Parks, Sean A., Lisa M. Holsinger, \textbf{Michael J. Koontz}, Luke Collins, Ellen Whitman, Marc-Andr\'e Parisien, Rachel A. Loehman, Jennifer L. Barnes, Jean-Fran\c{c}ois Bourdon, Jonathan Boucher, Yan Boucher, Anthony C. Caprio, Adam Collingwood, Ron J. Hall, Jane Park, Lisa B. Saperstein, Charlotte Smetanka, Rebecca J. Smith, and Nick Soverel. 2019. Giving ecological meaning to satellite-derived fire severity metrics across North American forests. \emph{Remote Sensing}. 11: 1735. \href{https://doi.org/10.3390/rs11141735}{https://doi.org/10.3390/rs11141735} \newline \textsuperscript{*}Editor's Choice article   
\newline I contributed to methodology, software, validation, review, and editing. & \tabularnewline

\hangindent=5ex 7. Smithers, Brian V., Meagan F. Oldfather, \textbf{Michael J. Koontz}, Jim Bishop, Catie Bishop, Jan Nachlinger, and Seema N. Sheth. 2019. Community turnover by composition and climatic affinity across scales in an alpine system. \emph{American Journal of Botany}. 107: 239-249. \href{https://doi.org/10.1002/ajb2.1376}{https://doi.org/10.1002/ajb2.1376}   
\newline I contributed to conceptualization, data curation, formal analysis, investigation, methodology, resources, software, supervision, validation, visualization, writing the original draft, review, and editing. & \tabularnewline
% \newline \emph{bioRxiv} preprint: https://doi.org/10.1101/659169 & \tabularnewline

\hangindent=5ex 6. \textbf{Koontz, Michael J.}, Meagan F. Oldfather, Brett A. Melbourne, and Ruth A. Hufbauer. 2018. Parsing propagule pressure: number, not size, of introductions drives colonization success in a novel environment. \emph{Ecology and Evolution}. 8 (16): 8043-8054. \href{https://doi.org/10.1002/ece3.4226}{https://doi.org/10.1002/ece3.4226}
\newline GitHub repository: \href{https://github.com/mikoontz/ppp-establishment}{https://github.com/mikoontz/ppp-establishment}   
\newline I contributed to conceptualization, data curation, formal analysis, funding acquisition, investigation, methodology, project administration, software, supervision, validation, visualization, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 5. Steel, Zachary L., \textbf{Michael J. Koontz}, and Hugh D. Safford. 2018. The changing landscape of wildfire: burn pattern trends and implications for California's yellow pine and mixed conifer forests. \emph{Landscape Ecology}. 33 (7): 1159-1176. \href{https://doi.org/10.1007/s10980-018-0665-5}{https://doi.org/10.1007/s10980-018-0665-5}   
\newline I contributed to formal analysis, investigation, methodology, software, validation, review, and editing. & \tabularnewline

\hangindent=5ex 4. Oldfather, Meagan F., Matthew N. Britton, Prahlad D. Papper, \textbf{Michael J. Koontz}, Michelle M. Halbur, Celeste Dodge, Alan L. Flint, Lorraine E. Flint, and David D. Ackerly. 2016. Effects of topoclimatic complexity on the composition of woody plant communities. \emph{AoB Plants}. 8: plw049. \href{https://doi.org/10.1093/aobpla/plw049}{https://doi.org/10.1093/aobpla/plw049}   
\newline I contributed to investigation, writing the original draft, review, and editing. & \tabularnewline

\hangindent=5ex 3. Hufbauer, Ruth A., Marianna Sz\"ucs, Emily Kasyon, Courtney Youngberg, \textbf{Michael J. Koontz}, Christopher Richards, Ty Tuff, and Brett A. Melbourne. 2015. Reply to Wootton and Pfister: the search for general context should include synthesis with laboratory model systems. \emph{Proceedings of the National Academy of Sciences}. 112 (44): E5904. \href{https://doi.org/10.1073/pnas.1517210112}{https://doi.org/10.1073/pnas.1517210112}   
\newline I contributed to conceptualization, writing the original draft, review and editing. & \tabularnewline

\hangindent=5ex 2. Hufbauer, Ruth A., Marianna Sz\"ucs, Emily Kasyon, Courtney Youngberg, \textbf{Michael J. Koontz}, Christopher Richards, Ty Tuff, and Brett A. Melbourne. 2015. Three types of rescue can avert extinction in a changing environment. \emph{Proceedings of the National Academy of Sciences}. 112 (33): 10557-10562. \href{https://doi.org/10.1073/pnas.1504732112}{https://doi.org/10.1073/pnas.1504732112}   
\newline I contributed to investigation, visualization, review, and editing. & \tabularnewline

\hangindent=5ex 1. Cole, Rebecca J., Creighton M. Litton, \textbf{Michael J. Koontz}, and Rhonda K. Loh. 2012. Vegetation recovery 16 years after feral pig removal from a wet Hawaiian forest. \emph{Biotropica}. 44: 463-471. \href{https://doi.org/10.1111/j.1744-7429.2011.00841.x}{https://doi.org/10.1111/j.1744-7429.2011.00841.x}   
\newline I contributed to investigation, review, and editing. & \tabularnewline

\end{longtable}