\begin{longtable}{@{} >{\raggedright}p{6.10in} >{\raggedleft} @{}}

\hangindent=5ex 4. \textbf{Koontz, Michael J.}, Victoria M. Scholl, Anna I. Spiers, Megan E. Cattau, John Adler, Joe McGlinchy, Tristan Goulden, Brett A. Melbourne, and Jennifer K. Balch. Democratizing macroecology: integrating uncrewed aerial systems with the National Ecological Observatory Network. Revisions requested for \emph{Ecosphere}. 
\newline GitHub repository: https://github.com/mikoontz/neon-drone-workflow & \tabularnewline

\hangindent=5ex 3. Mahood, Adam L., \textbf{Michael J. Koontz}, and Jennifer K. Balch. Fuel connectivity, burn severity, and seedbank survivorship drive the grass fire cycle in a semi-arid shrubland. Submitted to \emph{Ecology}. 
\newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.32942/osf.io/6x3as & \tabularnewline

\hangindent=5ex 2. Young, Derek J. N., \textbf{Michael J. Koontz}, and Jonah M. Weeks. Optimizing aerial imagery collection and processing parameters for drone-based individual tree mapping in structurally complex conifer forests. 
\newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.32942/osf.io/p7ygu & \tabularnewline

\hangindent=5ex 1. Joseph, Maxwell B., Anna I. Spiers, \textbf{Michael J. Koontz}, Nayani Ilangakoon, Kylen Solvik, Nathan Quarderer, et al. Ten simple rules for working with high resolution remote sensing data.
\newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.31219/osf.io/kehqz & \tabularnewline

% \hangindent=5ex 1. Joseph, Maxwell B., Anna I. Spiers, \textbf{Michael J. Koontz}, Nayani Ilangakoon, Kylen Solvik, Nathan Quarderer, Joe McGlinchy, Victoria M. Scholl, Lise St. Denis, Chelsea Nagy, Anna Braswell, Matthew W. Rossi, Lauren Herwehe, Leah Wasser, Megan E. Cattau, Virginia Iglesias, Adam Mahood, Fangfang Yao, Stefan Leyk, and Jennifer K. Balch. Ten simple rules for working with high resolution remote sensing data.
% \newline \emph{EcoEvoRxiv} preprint: https://doi.org/10.31219/osf.io/kehqz & \tabularnewline

\end{longtable}
